\section{Mandrill}
\label{sec:USR_mandrill}


Mandrill is a reliable, scalable, and secure delivery API for transactional emails from websites and applications. It's ideal for sending data-driven transactional emails, including targeted e-commerce and personalized one-to-one messages.
Trusted by more than 500,000 customers, Mandrill runs on a globally distributed infrastructure that can deliver emails in milliseconds.
Mandrill was developed by MailChimp, a company with more than 10 years of experience building a robust email marketing platform. MailChimp sends 15 billion emails every month for more than 8 million customers.


\subsubsection{Mailchimp}
\label{subsubsec:USR_mandrill_mailchimp}
MailChimp is the ultimate software that will change the way you market your product on the internet. MailChimp is a simple email marketing software (EMS) which gives you a number of easy options for designing, sending and saving templates of your emails. The number of feasible options and the easy to use interface set MailChimp apart from other software, and this can be seen with the number of users that use this software, going well over a million users.
MailChimp allows you to easily create newsletters of varying types and then provides simple options for sharing them on social networks such as Twitter or Facebook, making it your own personal platform for publishing your newsletter. Build a list of the people whom you want to market your products to, and save the list for use later on, and create custom templates for your products so that you do not have to rewrite mails again and again.
